Supplemental Material for: The evolution of gene expression in the term placenta of viviparous mammals

### 2016-09-23 manuscript/supplemental_material.Rnw
do gsea for morphology associations

\section{Gene Ontology Analyses}

>>>>

\section{GSEA}

\subsection{Pathway Analysis}
\begin{table}
<<pathway_analysis,echo=FALSE,results="asis">>=
pathway <- list()
for (database in c("kegg","reactome","biocarta","netpath")) {
    load(paste0("../data/placenta_gsea_",database))
    eval(parse(text=paste0("gsea.table <- placenta_gsea_",database)))
    gsea.table[,Database:=gsub("^(.)","\\U\\1",database,perl=TRUE)]
    pathway[[database]] <-
        gsea.table
}
pathway.analysis <-
    rbindlist(pathway)[fdr < 0.1,]
rm(pathway)
pathway.analysis[,Pathway:=gsub("^(KEGG|BIOCARTA|REACTOME) ","",
                                gsub("_+"," ",
                                     Pathway))]
pathway.analysis[,Pathway:=gsub(".+\\%","",Pathway)]

setnames(pathway.analysis,"p_values","p")
setorder(pathway.analysis,"p")
print(xtable(pathway.analysis,
             display=c("s","s","f","f","s"),
             align=c("c","p{2in}","r","r","c")),
      math.style.exponents=TRUE,
      include.rownames=FALSE,
      booktabs=TRUE,
      floating=FALSE)      
@ 
\caption[Core Placenta Pathway Enrichment]{Pathways with significant and suggestive enrichment
  ($\text{FDR}\le 0.1$) in the core placenta transcriptome using the
  biocarta, reactome, and kegg pathway databases}
\label{tab:core_placenta_pathway_analysis}
\end{table}

\begin{table}
<<pathway_analysis_class,echo=FALSE,results="asis">>=
pathway <- list()
for (class in c("shape","interdigitation","barrier")) {
    for (database in c("kegg","reactome","biocarta","netpath")) {
        load(paste0("../data/placenta_gsea_",class,"_",database))
        eval(parse(text=paste0("gsea.table <- placenta_gsea_",class,"_",database)))
        gsea.table[,Database:=gsub("^(.)","\\U\\1",database,perl=TRUE)]
        gsea.table[,Class:=gsub("^(.)","\\U\\1",class,perl=TRUE)]
        pathway[[paste0(class,"_",database)]] <-
            gsea.table
    }
}
placenta_class_gsea <-
    rbindlist(pathway)[fdr < 0.1,]
placenta_class_gsea[,Pathway:=gsub("^(KEGG|BIOCARTA|REACTOME) ","",
                                   gsub("_+"," ",
                                        Pathway))]
placenta_class_gsea[,Pathway:=gsub(".+\\%","",Pathway)]
setnames(placenta_class_gsea,"p_values","p")
setorder(placenta_class_gsea,"p")
print(xtable(placenta_class_gsea,
             display=c("s","s","f","f","s"),
             align=c("c","p{2in}","r","r","c")),
      math.style.exponents=TRUE,
      include.rownames=FALSE,
      booktabs=TRUE,
      floating=FALSE)      
@ 
\caption[Placenta Classification Pathway Enrichment]{Pathways with
  significant and suggestive enrichment ($\text{FDR}\le 0.1$) in genes
  associated with placenta morphology using the biocarta, reactome,
  and kegg pathway databases.}
\label{tab:core_placenta_pathway_analysis}
\end{table}

\subsection{GO Ontology}
